lab-meeting

### 2018-02-25 Report/lab-meeting.Rmd
Adds todo section

## Normalisation
Min normalising

@@

>>>>

## Preprocessing

So far no outliers have been removed
Paths haven't been smoothed
because of VR-real world differences, distances and times have been min-normalised

@@

# TODO

Get about 15-16 more participants. Not sure if 80 is necessary given current results.
Smooth paths and try to clean it enough to get less estimote dropouts
Remove outliers
Work with "wrong-door" stats

## Questions

Look are initial 3 trials performance after environment shift vs no shift

Look at progressive learning curve from block to block, rather than phase summaries

Add in the EEG
